{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}

### 2022-01-22 Paper/main.tex
Follow up on monomial basis

	\paragraph{Monomial Basis}
This is the basis that is needed in order to build polynomials, one of the best known ways of basis expansion.
For the polynomial of the form

	\begin{equation}
		f(t) = \sum_{i =1}^{\mathcal{I}} c_k(t -w)^{i-1}
	\end{equation}
	$(t -w)$ is the monomial basis function of the sequence

	\begin{equation}
		S_{i}^{MB}(t) = (t-w)^i, i = 0, 1, ..., \mathcal{I} 
	\end{equation}

	where the shift parameter $w$ usually is specified to be the center of the interval subject to approximation.

>>>>

	\paragraph{Monomial Basis}
This is the basis that is needed to build polynomials, one of the best-known ways to expand a function.
The polynomial of the form

	\begin{equation}
		f(t) = \sum_{k =1}^{K} c_k(t -w)^{k-1}
	\end{equation}
	can be expressed as a linear combination of the monomials $(t - w)$ which form the basis

	\begin{equation}
		S_{k}^{MB}(t) = (t-w)^k, k = 0, 1, ..., K.
	\end{equation}

	The shift parameter $w$ usually is specified to be the center of the interval subject to approximation.
